---
title: "Final Project"
author: "Team B - Yuval Sabag, Shani Bahat"
date: "13 6 2022"
output:
  pdf_document: default
  html_document: default
---

**In order to get our  end to end code analysis, run the chunks by the given order **

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Loading libraries
```{r load-packages, message = FALSE , include=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(janitor)
library(readxl)
library(parsnip)
library(plotly)
library(rsample)
library(yardstick)
library(widgetframe)
```

# 1.Loading & Cleaning the Data 

##### Please upload your data here
```{r}
followup_path <- "C:/Users/yuval/OneDrive/Desktop/F_project/data/MTurk Social Regulation Training - Followup Questionnaires_May 3, 2022_03.08.xlsx"

post_path <- "C:/Users/yuval/OneDrive/Desktop/F_project/data/MTurk Social Regulation Training - PostTraining Questionnaires_October 31, 2018_02.20.xlsx"
  
pre_provider_path <-"C:/Users/yuval/OneDrive/Desktop/F_project/data/MTurk Social Regulation Training - PreTraining Questionnaires Provider_October 31, 2018_02.14.xlsx"
  
pre_self_path <- "C:/Users/yuval/OneDrive/Desktop/F_project/data/MTurk Social Regulation Training - PreTraining Questionnaires Self_October 31, 2018_02.08.xlsx"

```


```{r, include=FALSE}

Follow_UP  <- read_excel(followup_path)

Post <- read_excel(post_path)

Pre_prov <- read_excel(pre_provider_path)

Pre_self <- read_excel(pre_self_path, sheet = "Sheet1")

```


##### Rename columns and delete unrelated lines
```{r}
Follow_UP <- Follow_UP[3:49, ]

names(Follow_UP)[19:40]<- paste0(rep("", each=22), "RRS_",1:22)

names(Follow_UP)[41:60]<- paste0(rep("", each=20), "CES.D_",1:20)
```


##### Handling relevant columns - FollowUP data
```{r}

Follow_UP <- select(Follow_UP, WorkerID, contains("CES.D_"),contains("RRS_"), Gender, SES_Degree)%>% mutate_at(c(2:45), as.numeric) %>% rowwise()%>% mutate(FollowUP_CES.D_sum = sum(c_across(contains("CES.D_"))), FollowUP_RRS_sum = sum(c_across(contains("RRS_"))) ) 


Follow_UP <- select(Follow_UP, WorkerID, FollowUP_RRS_sum, FollowUP_CES.D_sum, Gender, SES_Degree)

Follow_UP <- na.omit(Follow_UP)

```


##### Handling relevant columns - Post data
```{r}
Post <- select(Post, WorkerID, PostTraining_RRS_sum,contains("CES.D_"))%>% rowwise()%>% mutate(PostTraining_CES.D_sum =sum(c_across(contains("CES.D_"))))

Post <- select(Post, WorkerID, PostTraining_RRS_sum, PostTraining_CES.D_sum) 

Post <- na.omit(Post)

```


##### Handling relevant columns - Pre provider data
```{r}
Pre_prov <- select(Pre_prov, WorkerID,group, RRS_sum,contains("CES.D_"))%>% rowwise()%>% mutate(Pre_CES.D_sum =sum(c_across(contains("CES.D_"))),Pre_RRS_sum = RRS_sum )

Pre_prov <- select(Pre_prov, WorkerID, group, Pre_RRS_sum, Pre_CES.D_sum) 

Pre_prov <- na.omit(Pre_prov)

```

##### Handling relevant columns - Pre self data
```{r}
Pre_self <- select(Pre_self, WorkerID, group, RRS_sum,contains("CES.D_"))%>% rowwise()%>% mutate(Pre_CES.D_sum =sum(c_across(contains("CES.D_"))),Pre_RRS_sum = RRS_sum )

Pre_self <- select(Pre_self, WorkerID, group, Pre_RRS_sum, Pre_CES.D_sum) 

Pre_self  <- na.omit(Pre_self)
```

##### Merge two tables (Pre provider, Pre self ) into one - Pre
```{r}
Pre <- full_join(Pre_self, Pre_prov, by = c("WorkerID", "group", "Pre_RRS_sum", "Pre_CES.D_sum"))

```

##### Merge all the tables into one table - Data
```{r}
#Dropping duplicate. 
#Change of variables of Gender: 0 - for men and 1 - for women .
#Change data type of Gender into factor .

Data <- inner_join(inner_join(Pre, Post, by = c ("WorkerID")), Follow_UP, by = c ("WorkerID")) 

Data <- Data %>% distinct(WorkerID, .keep_all = TRUE)


Data$Gender[Data$Gender== "0"] <- "Male"

Data$Gender[Data$Gender== "1"] <- "Female"

Data <- Data %>%  mutate(Gender = factor(Gender))

```



##### Remove outliers
```{r}
outliers1 <- boxplot(Data$FollowUP_CES.D_sum, plot = FALSE)$out

outliers2 <- boxplot(Data$PostTraining_CES.D_sum, plot = FALSE)$out

outliers3 <- boxplot(Data$Pre_CES.D_sum, plot = FALSE)$out
```


```{r}
Data <- Data[-which (Data$FollowUP_CES.D_sum %in% outliers1), ]

Data <- Data[-which (Data$PostTraining_CES.D_sum %in% outliers2), ]

Data <- Data[-which (Data$Pre_CES.D_sum %in% outliers3), ]
```



##### Handling relevant columns
```{r}
Data <- select(Data, WorkerID, group, Gender, SES_Degree, Pre_RRS_sum, Pre_CES.D_sum, PostTraining_RRS_sum, PostTraining_CES.D_sum, FollowUP_RRS_sum, FollowUP_CES.D_sum)

glimpse(Data)
```



# 2.Data Analysis 

##### Summary Statistic
```{r}
rrs <- Data %>% pivot_longer(!c(WorkerID,SES_Degree,group,Gender,Pre_CES.D_sum,PostTraining_CES.D_sum,FollowUP_CES.D_sum), names_to = "Period", values_to = "RRS")%>% select(WorkerID, Gender, Period, RRS)  


rrs$Period[rrs$Period == c("Pre_RRS_sum", "PostTraining_RRS_sum", "FollowUP_RRS_sum")] <- c("Pre", "Post", "Follow_UP")

```


```{r}
ces.d <- Data %>%  pivot_longer(!c(WorkerID,SES_Degree,group,Gender,Pre_RRS_sum,PostTraining_RRS_sum,FollowUP_RRS_sum), names_to = "Period", values_to = "CES.D") %>% select(WorkerID, Gender, Period, CES.D)

ces.d$Period[ces.d$Period == c("Pre_CES.D_sum", "PostTraining_CES.D_sum", "FollowUP_CES.D_sum")] <- c("Pre", "Post", "Follow_UP")

```


```{r}
stat <- inner_join(rrs, ces.d, by = c("WorkerID", "Gender", "Period"))

stat
```



###### RRS and CES.D rates scattering By period of time
```{r, fig.width=6, fig.height=2.75}

ggplot(stat, aes(x = RRS, y = CES.D, color = Period))+
  labs(x = "RRS rate ", y = "CES.D rate", title = "RRS and CES.D rates scattering", subtitle = "By period of time")+
  facet_grid(~factor(Period, levels = c("Pre", "Post", "Follow_UP")))+
  geom_point()+
  theme_bw()+
   theme(legend.position = "bottom")+
  scale_color_manual(labels = c("2 Months Followup", "Post", "Pre"), values = c("darkslategrey", "darkslategray4", "darkslategray3"))
```


###### CES.D RATE By period of time & RRS RATE By period of time
```{r, figures-side, fig.show="hold", out.width="50%"}
#CES.D
ggplot(stat, aes(x=Period, y=CES.D, fill= Period))+
  labs(y = "CES.D rate", title = "CES.D RATE", subtitle = "By period of time")+
  geom_boxplot(varwidth = TRUE)+
  scale_x_discrete(limits = rev)+
  theme_bw()+
  theme(legend.position = "bottom")+
   scale_fill_manual(labels = c("2 Months Followup", "Post", "Pre"), values = c("darkslategrey", "darkslategray4", "darkslategray3"))


#RRS 
ggplot(stat, aes(x=Period, y=RRS, fill= Period))+
  labs(y = "RRS rate", title = "RRS RATE", subtitle = "By period of time")+
  geom_boxplot(varwidth = TRUE)+
  scale_x_discrete(limits = rev)+
  theme_bw()+
  theme(legend.position = "bottom")+
  scale_fill_manual(labels = c("2 Months Followup", "Post", "Pre"), values = c("darkslategrey", "darkslategray4", "darkslategray3"))
  
```


##### Summary Statistics

```{r}
summary(stat)
```


```{r}
stat %>% group_by(Period) %>% summarise(mean_RRS = mean(RRS), mean_CES.D = mean(CES.D))
```



#### 3.Model fit

##### Splitting data to train and test ans set seed
```{r}
set.seed(24)

#Put 90% of the data into the training set
data_split <- initial_split(Data, prop = 0.90)

#Create data frames for the two sets
train_data <- training(data_split)
test_data <- testing(data_split)
```

##### Peek at the split
```{r}
glimpse(train_data)
```

```{r}
glimpse(test_data)
```



##### Build linear regression
```{r}
fit <- lm(FollowUP_RRS_sum ~ Pre_RRS_sum + Pre_CES.D_sum + Gender, data = train_data)

summary(fit)
```


##### Creating surface to 3D plot
```{r}
x <- seq(1, 100, by = 2)
y <- seq(1, 100, by = 2)

plane <- outer(x, y, function(a,b){9.0327 +  0.6293*a + 0.3277 *b})

male <- outer(x, y, function(a,b){9.0327 +  0.6293*a + 0.3277 *b -3.3736}) 
```


##### Fit a model to the traning dataset 
```{r}
data_fit <- linear_reg() %>%
  set_engine('lm') %>%
  fit(FollowUP_RRS_sum ~ Pre_RRS_sum + Pre_CES.D_sum + Gender, data = train_data)

glance(data_fit)$adj.r.squared
```


Can be seen only in R and not in html/PDF

```{r , warning=FALSE}

p <- plot_ly(train_data, x = ~Pre_RRS_sum, y = ~Pre_CES.D_sum, z = ~FollowUP_RRS_sum, color = ~Gender,colors = c("darkslategrey", "darkslategray3"),
marker = list(size = 3, alpha = 0.5,line = list(color = "white" ,width = 0.3))) %>% add_markers() %>% 
add_surface(x= ~x, y= ~y, z= ~plane, type = "surface", colorscale = list(c(0, 1), c("rgb(174, 235, 235)", "rgb(174, 235, 235)")), opacity = 0.7, showscale = FALSE, hovertemplate = paste0('Pre_RRS: %{x}<br>', "Pre_CES.D: %{y}<br>", "Pred_RRS: %{z}<br>" )) %>% 
add_surface(x= ~x, y= ~y, z= ~male, type = "surface",name = "Male",colorscale = list(c(0, 1), c("rgb(72, 87, 87)", "rgb(72, 87, 87)")), opacity = 0.5, showscale = FALSE, hovertemplate = paste0('Pre_RRS: %{x}<br>', "Pre_CES.D: %{y}<br>", "Pred_RRS: %{z}<br>"))

frameWidget(p)


```


# 4.Test the Model

##### Predict on the testing dataset
```{r}
test_pred <- predict(data_fit, test_data) %>% bind_cols(test_data %>% select(FollowUP_RRS_sum, Pre_RRS_sum, Pre_CES.D_sum, Gender))

test_pred
```


##### RMSE index
```{r}
rmse(test_pred, truth = FollowUP_RRS_sum, estimate = .pred)
```

##### R- squared index
```{r}
rsq(test_pred, truth = FollowUP_RRS_sum, estimate = .pred)
```





